### 2025-07-14 paper/sections/intro.qmd
all addressed except stat sign

Specifically, **we propose Counterfactual Training (CT)**: a novel training regime explicitly geared towards improving the explanatory capacity of models that, in high-level terms, we define as the extent to which valid explanations derived for a model can be deemed plausible with respect to the underlying data and global actionability constraints (we refine this notion in Def. \ref{def-explainability}). For simplicity, we refer to models with high explanatory capacity as *explainable*. To the best of our knowledge, Counterfactual Training represents the first attempt to achieve more explainable models by employing counterfactual explanations already in the training phase.

>>>>

Specifically, **we propose Counterfactual Training (CT)**: a novel training regime explicitly geared towards improving the explanatory capacity of models that, in high-level terms, we define as the extent to which valid counterfactual explanations derived for a model can be deemed plausible with respect to the underlying data and global actionability constraints (we refine this notion in Def. \ref{def-explainability}). To the best of our knowledge, Counterfactual Training represents the first attempt to achieve more explainable models by employing counterfactual explanations already in the training phase.
